---
title: "Setting Up the c19randepimod package"
Author: Pedro Nascimento de Lima
output:
  pdf_document: default
  rmarkdown::html_vignette: default
vignette: >
  %\VignetteIndexEntry{Package Set Up}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This short tutorial goes over the process of installing the package and calibrating the model for a single state.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Installation

First, download the source package (.tra.gz file) from the git repository. Then, install it using the `install_local` function from the `devtools` package.

```{r}

# If devtools is not isntalled, install it first:

# install.packages(devtools)

# devtools::install_local("C:/dev/covid-19/c19randepimod_1.0.0.tar.gz")

```


# Setting Up Inputs Files

Before running the model, the package reads inputs from three excel spreadsheets. You can create a folder for your analysis by running the `setup_c19_folder` function. This function you create the inputs file you will need to run the model.

```{r}
library(c19randepimod)
library(dplyr)

# This function creates a folder and inputs files you need to run the model:
setup_c19_folder(path = "analysis", overwrite =T) 

```

Once you have your inputs file in place, you can use the `get_augmented_inputs` function, which will be the backbone of your model.

```{r}
# This function creates a folder and inputs files you need to run the model:
augm_inputs = get_augmented_inputs(inputs_path = "./analysis/template_analysis/inputs")

```

# Calibrating the Model

Now you can create the model and Run the Calibration Process:

```{r}

model = augm_inputs %>%
  prepare_inputs(.) %>%
  c19model_amshi2s(., level = "state") %>%
  calibrate(model = ., location_ids = 35, n_lhs = 2, parallel_mode = "PSOCK", cores = 2) %>%
  compute_augmented_outputs(model = ., compute_econ_outputs = T, calibration = T)

```

Finally, plot the calibration results:

```{r}

plot(model)

```