---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# c19randepimod

<!-- badges: start -->
[![License: GPL-2](https://img.shields.io/badge/license-GPL--2-blue.svg)](https://cran.r-project.org/web/licenses/GPL-2)
[![](https://img.shields.io/badge/doi-10.7249/TLA173--1-purple.svg)](https://doi.org/10.7249/TLA173-1)

<!-- badges: end -->

This is the R package behind [RAND's COVID-19 State policy Evaluation Tool](https://www.rand.org/pubs/tools/TLA173-1/tool.html). This package contains code that reads data from external APIs, calibrates the epidemiological model, runs the model for pre-specified scenarios and saves these results. This R package does not contain code for the webtool Frontend and the econ model.

## Installation

First, download the R package from the git repository. You can install the package from source using:

```{r installation, eval=FALSE}

# If you don't have devtools installed, install it first (make sure to )
# install.packages("devtoools")

devtools::install_local(path = "c19randepimod_1.0.0.tar.gz",upgrade = "never")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(c19randepimod)
## basic example code
```

